\section{Discussion}
The binary classification problem was easily solved.
Using a ResNet18 with transfer learning and default transforms quickly reached high performance.
I found that classifying if a fish was present or not to be a much easier problem than identifying the kind of fish in the image.
The dataset itself was well structured for the fish or no fish problem. Meaning that it was well balanced.

Identifying the fish species introduced complexity. One problem it introduced was the balance of the data. 
The 17 classes introduced do not have the same balance that the previous fish or no fish classes maintained.
Table \ref{tab:fish_classes} shows that Fish1 has several times the samples as half of the dataset.  
Also, the no fish class still exists as a image could not contain a picture of a fish. 
It maintains its large number of samples and suddenly there is a big balance problem!
I tried to solve this by adjusting the sampling but simply ran out of time to adjust and record in a meaningful way.
The confusion matrices in the Results section such as \ref{fig:res18weightsconf} show that the no fish class is collecting predictions, this makes it apparent that the no fish class was a safe place for the model to predict if it was unsure of the fish.
A example of why this might be happening can be seen in figure \ref{graphic:fishexample} the image at first glance seems to not have a fish, but it is in the upper right hand corner.
Its possible that this image looks like one where a fish isn't present to the model.

Transfer Learning helped increase performance significantly. In every model it improved the accuracy by 20\%.  
Ajusting the batch size also effected the sample size. For the models, I found having a large batch of more than 128 negatively effected accuracy. I settled with the smaller batch size for most of the models for both performance and hardware restrictions. I was unable to train larger models with large batch sizes without running out of GPU RAM.
